\color{navyblue} Difference-in-Differences Estimation with Spatial Spillover

### 2021-02-12 latex/paper/Spillover.tex
Rework Introduction

\title{\color{navyblue} Differences-in-Differences with Spatial Spillover}
% \subtitle{Subtitle}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}

@@

    \begin{abstract}
        Empirical work often uses treatment variables defined by geographic boundaries. When researchers ignore the common problem that the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect. In this paper, I decompose this bias in two parts. First, the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment. Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. I use Monte Carlo simulations to demonstrate when the biases are particularly large. Further, I show that a common solution used in the literature of removing `contaminated' control units only prevents the first source of bias. Lastly, I propose improved estimation strategies that can remove both sources of bias. I highlight the importance of considering spillovers by revisiting analysis of the Tennessee Valley Authority.
    \end{abstract}
\end{titlepage}
% ------------------------------------------------------------------------------

@@

Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states. Potentially, the effect of these treatments do not stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects influencing neighboring areas. Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously. In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run difference-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} In this paper, I show that failing to account for spatial spillovers can lead to poorly identified estimates of treatment effects.

In the causal inference literature, researchers assume that a unit's potential outcome does not depend on the treatment status of any other unit -- what \citet{Rubin_1980} calls the Stable Unit Treatment Value Assumption (SUTVA). This article considers a common violation of SUTVA in a process I label `spatial spillovers' where the treatment assignment of `close' units' affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g. geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} Typically researchers are interested in the `direct effect' on the treated units.\footnote{This is sometimes called the `partial equilibrium' effect or the `local effect'.} In the presence of spatial spillovers, I show using a potential outcomes framework that the difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.

The intuition for the two bias terms resulting from spillovers is as follows. First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes. In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, consider a factory opening in a county. Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain \citep{Duranton_Puga_2003}. The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment. Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had a welfare function that included both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units. Difference-in-differences estimation would therefore result in double undercounting.}

Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. The spillover onto other treated units is averaged into the treated units' change in outcomes. Therefore the bias of treatment effect is the same sign as the sign of the spillover. Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces. The estimated treatment effect will count the `direct` effect of the factory opening as well as the benefit of the agglomeration economies. Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.

These biases can be written as functions of the potential outcomes in my framework and can be used by researchers to sign or bound the bias using insight from their economic context. The magnitude of the bias depends on two factors: the size of the spillovers and the number of units affected by spillovers. If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large. Th results of this paper enable researchers to estimate bounds for it by making assumptions about the average size of the spillover effect and the number of units affected. I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.

In the survey by \citet{Berg_Streitz_2019}, only eight of the 21 papers that discuss spillovers control for this potential source of bias in their primary empirical specification to prevent bias in the estimation of treatment effects. The other thirteen papers usually first estimate the direct effect without controlling for spillovers and then seperately estimate the spillover effects. This paper shows that not controlling for spillovers produces biased estimates of the direct effect.

Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers. Since this is a common strategy used by researchers, I use Monte Carlo simulations to show that this method is effective in the case where spillovers \textit{only} occur onto control units. In the presence of spillover onto also treated units, the estimates for the direct effect will still be biased. Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.

Removing both sources of bias requires a researcher to take a stance and parameterize a functional form for the spillovers. The particular functional form depends on the context of the application. However, there are a few practical considerations. First, the researcher should argue whether spillovers on control units and on treated units exist. Second, they should argue what the maximum distance these spillovers can occur. Last, they should consider if spillovers are additive in the number of nearby units that are treated.

In section \ref{sec:monte_carlo}, I use Monte-Carlo simulations to emphasize when misspecificied spillovers still remove most of the bias and when they fail to do so.

% @TODO: Discuss effectiveness under misspecification of spillovers (correct distance and additive/non-additive).

% ------------------------------------------------------------------------------
\subsection{Contribution}
% ------------------------------------------------------------------------------

The literature considering spillovers primarily has focused on ``within-group'' spillovers where units are in distinct groups and outcomes depend on the treatment status within the observation's group only.\footnote{For example, researchers consider peer effects within schools. In this case, each school constitutes a group and it is assumed that outcomes do not depend on other schools' treatment status, i.e. SUTVA is satisfied between-groups. Estimation of spillover effects in this case is done in a `partial intereference' framework that compares ``control'' units in a partially treated group with control units in completely untreated groups. \citet{Angelucci_DiMaro_2016} provides a summary for estimation of spillover effects in within-group settings. Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} However, spatial settings such as counties do not feature distinct groups which allow for the researcher to separate areas into distinct non-overlapping groups (a county is connected to all other counties by some chain of neighbors). My paper considers a more general form of interference. Identification in this framework requires the researcher to either identify control units that are free from spillovers (far-away from treatment) or to parameterize how control units are affected by treatment.

\citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector. He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h(\vec{D}, i)$. The function $h(\vec{D}, i)$ is referred to as an exposure mapping and adding this to the potential outcomes framework allows me to explicitly model SUTVA violations. Using this framework, \citet{Vazquez-Bare_2019} shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.

My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by difference-in-differences.

\citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''. That is, a treated unit's treatment effect is defined as the direct effect \textit{and} the general equilibrium spillover effects. Then, the authors describe how the average treatment effect (ATE) estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h(\vec{D}, i)$. My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.\footnote{These estimates can be combined afterwards to estimate their definition of average treatment effect. The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.}

There are a few papers that discuss estimation of treatment effects with spatial spillovers using the difference-in-differences framework. \citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model. However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units. \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} identifies biases in estimation of the direct effect for a specific potential outcome function where $h(\vec{D}, i)$ is the proportion of treated contiguous counties. Finally, \citet{Delgado_Florax_2015} consider the case where the exposure mapping is defined by a spatial weights matrix $W\vec{D}$ that enters linearly into the potential outcomes. This does not allow for the coefficient to change for control and treated units.\footnote{Although, one could change the weighting matrix to make ad-hoc assumption of the signs and relative magnitudes of spillovers onto treated and control units, but this allows for less data-driven estimation.}

My paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers. For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly. My paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.

Lastly, I contribute to a literature in urban economics on local place-based policies. Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects. I contribute to estimating aggregate effects of place-based policies by showing that typical estimation strategies can underestimate the local effect by ignoring spillovers. As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}. The Tennessee Valley Authority was a large push to bring electrification to the Tennessee Valley with the goal of improving the manufacturing sector there. The scale of the program was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies. I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.

@@

Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards. This framework can be extended in section \ref{sec:event_study}. As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The potential outcomes are denoted $Y_{i,t}(D_i, h(\vec{D}, i)$). The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function. The exposure mapping measures the intensity at which unit $i$ is affected by spatial spillovers. When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = 0$. The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment as summarized by $h(\vec{D}, i)$. To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature.

First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.  In this case \begin{equation}\label{eq:h_within}
    h(\vec{D}, i) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
\end{equation}
This exposure mapping is useful when it is assumed that spillovers do not decay over distance until $\bar{d}$ and the number of neighboring units treated do not impact the intensity of spillovers. For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library. Access to a neighboring town library is binary in nature, so it does not matter whether you can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.

Second, $h(\vec{D}, i)$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \begin{equation}\label{eq:h_within}
    h(\vec{D}, i) = 1/k \sum_{j \in K(i)} D_j,
\end{equation}
where $K(i)$ is the index of unit $i$'s k-nearest neighbors. This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of units treated. In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies. As more nearby counties receive new stores, the agglomeration forces increase \citep{Basker_2005}.

Last, is the spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \begin{equation}\label{eq:h_decay}
    h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
\end{equation} 
This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using non-linear least squares. In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.

@@

With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0).
\] 
The spillover measures the difference in non-treated potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed. Then, the average spillover effect onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0) \ \vert \ D_i = 0 \right].
\]

@@

It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences. I assume that what the `average treatment effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, 0) - Y_{it}(0, 0) \ \vert \ D_i = 1 \right],
\] 
which measures the effect of being treated in the absence of exposure to spillovers. This effect does not include the general equilibrium effects of multiple treated areas near one-another.

@@

In this section, I identify the two sources of bias in difference-in-differences estimation of the direct effect of treatment. For exposition, I will refer to one pre- and post-period, $t = 0$ and $t = 1$, but this can be replaced by averages across $Y$ in the pre-period and the post-period respectively. To estimate the `direct effect of treatment', researchers estimate the canonical two-way fixed effects model, 
\begin{equation}\label{eq:twfe}    
    y_{it} = \tau D_{it} + \mu_i + \mu_t + \epsilon_{it}.
\end{equation}

@@

\begin{assumption}[Parallel Counterfactual Trends]\label{eq:parallel}
    \[ 
        \mathbb{E}\left[ Y_{i1}(0, 0) - Y_{i0}(0, 0) \ \vert \ D_i = 1 \right] = 
        \mathbb{E}\left[ Y_{i1}(0, 0) - Y_{i0}(0, 0) \ \vert \ D_i = 0 \right]
    \]
\end{assumption}
This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status. This generalizes to the classic parallel counterfactual trends when SUTVA is satisfied because then every unit has zero exposure.

Given that Assumption (\ref{eq:parallel}) holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias. The proof is given in Appendix \ref{sec:proofs}.

\begin{theorem}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
    If Assumption (\ref{eq:parallel}) holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
    \begin{align*}
        \mathbb{E}[\hat{\tau}] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right]}_{\text{Difference-in-Differences}} \\ 
        &= 
        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
        &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
        &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
    \end{align*}
\end{theorem}

@@

First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatmnet if the potential outcomes are correctly specified. In the case where potential outcomes are `somewhat' incorrectly specified, this can remove some of the bias in estimation. Simulations below highlight that since spillovers are likely to decay over distance, controlling for immediate neighbors removes a large portion of the average spillover effects.

>>>>

\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillover}
% \subtitle{Subtitle}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}

@@

    \begin{abstract}
        Empirical work often uses treatment variables defined by geographic boundaries. When researchers ignore the common problem that the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect. In this paper, I decompose this bias in two parts. First, the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment. Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. I propose estimation strategies that can remove both sources of bias as well as semi-parametrically estimate the spillovers themselves. Lastly, I extend this estimation strategy in an event-study framework following \citet{Callaway_Sant’Anna_2020}. Then, I turn to an empirical application revisiting an analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}. I highlight the importance of considering general equilibrium spillovers in the analysis of place-based policies when estimating the direct effect on targeted areas.
    \end{abstract}
\end{titlepage}
% ------------------------------------------------------------------------------

@@

Empirical work in economics often considers treatment assigned to groups of units, but the effect of these treatments potentially do not stay within these groups and spillover onto ‘close’ units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g. geographic
distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, treatment is often assigned to geographic boundaries and spillovers occur from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects influencing neighboring areas. Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.\footnote{The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect. In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The central result of my paper is that in the presence of spillovers, the difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.

The intuition for the two bias terms resulting from spillovers is as follows. First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes. In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, consider trying to estimate employment effects of a factory opening in a county. Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain which would potentially increase employment \citep{Duranton_Puga_2003}. The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment. Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had a welfare function that included both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units. Difference-in-differences estimation would therefore result in double undercounting.}

Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. The spillover onto other treated units is averaged into the treated units' change in outcomes. Therefore the bias of treatment effect is the same sign as the sign of the spillover. Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces. The estimated treatment effect will count the `direct' effect of the factory opening as well as the benefit of the agglomeration economies. Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.

I then propose an estimation strategy that will remove both sources of bias with very minimal assumptions on the structure of spillovers. To remove \textit{all bias} from the direct effect estimate, a research needs to just include an indicator for being close to a treated unit interacted with treatment status, so long as the indicator captures all units affected by spillovers. An indicator removes all bias because in my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units. The interacted indicator will estimate this average and remove both bias terms from the treatment effect estimate. Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space. The only assumption required is the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed. However, including too many units will increase the variance in the estimates for average spillover effects.}

Since spillovers themselves are often important causal effects themselves, I next turn to how to estimate spillovers directly. I show with evidence from Monte Carlo simulations, that commonly used semi-parametric estimation strategies capture spillovers well (in a mean square prediction error sense). This involves creating a set of distance bins from treated units (e.g. being 0-20 miles, 20-40 miles, 40-60 miles from treated unit). The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not. For non-additive spillovers, I recommend a set of mutually-exclusive indicators for the closest treated unit being in each distance bin. For additive spillovers, I recommend using the number of treated units within each spillover bin.

As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}. The Tennessee Valley Authority was a large scale New Deal program that created many new dams for flood-protection and navigation. The construction of large-scale dams lowered the cost of power for industrial firms giving the region an industrial boost \citep{Kitchens_2014}. The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citet{Severnini_2014}. I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.

I turn to an empirical application in the literature in urban economics on local place-based policies in section \ref{sec:tva}. Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects in non-treated locations. I contribute by showing that because of these general equilibrium effects, estimation of local effects are often underestimated by not controlling for the spillover effects in estimation.

Last, in section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_Sant’Anna_2020}. I first show how to adjust their methods to control for spatial spillovers in estimation of treatment effects. Second, I show how an extension of their method allows for estimation of spillover effects. My paper is the first paper to study estimation of treatment effects in an event-study framework.

There is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers. Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares untis in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects. This allows standard difference-in-differences estimation of both the direct effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).

More recently, a new strand of literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster by using a potential outcomes framework. \citet{Vazquez-Bare_2019} presents a potential outcomes model that explicitly accounts for ``within-group'' spillovers in experiments which allows for seperate estimation of direct effect and spillover effects by a simple differences-in-means. I extend this work by focusing on difference-in-differences estimation in non-experimental settings.  \citet{Sävje_Aronow_Hudgens_2019} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects. My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.These estimates can be combined afterwards to estimate their definition of average treatment effect. The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.

I also contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}. I contribute to this literature in two ways. First, my paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers. For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly. Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.

@@

Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards. This framework is extended to staggered treatment adoption in section \ref{sec:event_study}. Potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The potential outcomes are denoted $Y_{i,t}(D_i, h(\vec{D}, i)$). The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function. The exposure mapping measures the intensity at which unit $i$ is affected by spatial spillovers. When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$. The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment as summarized by $h(\vec{D}, i)$. To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature.

\begin{example}
    First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.  In this case \begin{equation}\label{eq:h_within}
        h(\vec{D}, i) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
    \end{equation}
    This exposure mapping is useful when it is assumed that spillovers do not decay over distance until $\bar{d}$ and the number of neighboring units treated do not impact the intensity of spillovers. For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library. Access to a neighboring town library is binary in nature, so it does not matter whether you can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.  
\end{example}

\begin{example}
    Second, $h(\vec{D}, i)$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
        h(\vec{D}, i) = \sum_{j} D_j * 1[ d(i,j) < \bar{d} ].
    \end{equation}
    This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of nearby units treated. In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies. As more nearby counties receive new stores, the agglomeration forces increase \citep{Basker_2005}.
\end{example}

\begin{example}
    Last, is the spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \begin{equation}\label{eq:h_decay}
        h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
    \end{equation} 
    This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using non-linear least squares. In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure. 
\end{example}

@@

With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, \vec{0}).
\] 
The spillover measures the difference in non-treated potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed. Then, the average spillover effect onto control units averages over potential heterogeneity in the effect size of spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, \vec{0}) \ \vert \ D_i = 0 \right].
\]

@@

It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences. I assume that what the `average treatment effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, \vec{0}) - Y_{it}(0, \vec{0}) \ \vert \ D_i = 1 \right],
\] 
which measures the effect of being treated in the absence of exposure to spillovers. This effect does not include the general equilibrium effects of multiple treated areas near one-another.

@@

In this section, I identify the two sources of bias in difference-in-differences estimation of the direct effect of treatment. To estimate the `direct effect of treatment', researchers estimate the canonical two-way fixed effects model, 
\begin{equation}\label{eq:twfe}    
    y_{it} = \tau D_{it} + \mu_i + \mu_t + \epsilon_{it}.
\end{equation}

@@

\begin{assumption}[Parallel Counterfactual Trends]\label{eq:parallel}
    \[ 
        \mathbb{E}\left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1 \right] = 
        \mathbb{E}\left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0 \right]
    \]
\end{assumption}
This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status. This generalizes to the classic parallel counterfactual trends when SUTVA is satisfied because then every unit has zero exposure.

Given that Assumption \ref{eq:parallel} holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias. The proof is given in Appendix \ref{sec:proofs}.

\begin{proposition}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
    If Assumption \ref{eq:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
    \begin{align*}
        \mathbb{E}[\hat{\tau}] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right]}_{\text{Difference-in-Differences}} \\ 
        &= 
        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
        &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
        &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
    \end{align*}
\end{proposition}

@@

First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatment if the potential outcomes are correctly specified. In the case where potential outcomes are `somewhat' incorrectly specified, this can remove some of the bias in estimation. Simulations below highlight that since spillovers are likely to decay over distance, controlling for immediate neighbors removes a large portion of the average spillover effects even under misspecification.
